\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables


% Copyright
\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
%\acmDOI{10.475/123_4}
\acmDOI{}


% ISBN
%\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[PCSC2017]{Philippine Computing Science Congress}{March 2017}{Cebu City, Philippines} 
\acmYear{2017}
\copyrightyear{2017}

\acmPrice{}

\begin{document}
\title{SkyLab : An extensible workflow web application for HPC on the cloud}

\author{Vincent Paul L. Carpio}
\affiliation{%
  \institution{Institute of Computer Science\\ 
	College of Arts and Sciences \\
	University of the Philippines Los Banos  
  }
}
\email{vlcarpio@up.edu.ph}

\author{Katrina Joy M. Abriol-Santos}
\affiliation{%
  \institution{Institute of Computer Science\\ 
	College of Arts and Sciences \\
	University of the Philippines Los Banos  
  }
}
\email{khmagno@up.edu.ph}

\author{Joseph Anthony C. Hermocilla}
\affiliation{%
  \institution{Institute of Computer Science\\ 
	College of Arts and Sciences \\
	University of the Philippines Los Banos  
  }
}
\email{jchermocilla@up.edu.ph}



% The default list of authors is too long for headers}
\renewcommand{\shortauthors}{V. P. Carpio et. al.}


\begin{abstract}
Most scientific applications require high performance computing (HPC) which utilizes parallel processing to run tasks quickly and efficiently. MPI clusters are often used to cater this type of tasks but the hardware required can be costly. Peak-Two Cloud (P2C) can host HPC applications in a cloud environment which is relatively cheaper due to resource reuse and more convenient due to on-demand provisioning. One of the key features of P2C is vCluster, a tool that can deploy MPI clusters usable through the command line. In this paper, we present the design and implementation, as well as user-evaluation results of SkyLab, a workflow web application on top of vCluster to simplify the process of running MPI applications for users not accustomed to the command line. SkyLab currently supports applications used in bioinformatics, molecular dynamics, molecular docking, and quantum chemistry. The extensible design of SkyLab enables additional tools to be incorporated easily as modules. 
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>  
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

% We no longer use \terms command
%\terms{Theory}

\keywords{cloud computing, high performance computing, web interface}


\maketitle

\input{carpio-pcsc2017-skylab-body}

\bibliographystyle{ACM-Reference-Format}
\bibliography{carpio-pcsc2017-skylab} 

\end{document}
